Bee visitation, pollination services, and plant yield in commodity and hybrid seed canola

### 2022-06-20 Manuscript/main.tex
Worked on commodity models

\subsection{Data collection}
From June through August of 2014 and 2015, we surveyed 29 commodity canola fields (14 in 2014, 15 in 2015) near Beaverlodge, Alberta and 31 fields (17 in 2014, 14 in 2015) near Lethbridge, Alberta.
Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
28 of the 60 fields were stocked with honey bees at the corner or side of the field (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked. %range: 0.03 - 3.1 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
14 of 31 of the fields near Lethbridge were watered using central-pivot irrigation systems.
% Growers were asked for canola variety information, but there was not enough replication to test for difference between varieties. 
% Fields with central-pivot irrigation were mostly circular, but dryland (non-irrigated) fields were usually square or rectangular.

%Maps + climate graphs needed for publication
During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year.
Seed fields were all stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with leafcutter bees in shelters throughout the field.
Shelters used either ``standard" or ``double"  leafcutter bee stocking ($\approx$50,000 vs. 100,000 cocoons/ha), and shelters were placed at either ``standard" or ``double" densities (1.3 vs. 2.6 shelters/ha) in each field.
Double stocking rates were only used in fields with double shelter density, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
All seed fields had central-pivot irrigation, and were mostly circular or semi-circular in shape.
%Woudick 5,6 = 64 shelters (single), Woudick 2 = 113 shelters (double + bees), Woudick 3 = 128 shelters Graham 1 = 135 shelters

>>>>

\subsection{Data collection}
From June through August of 2014 and 2015, we surveyed 29 commodity canola fields (14 in 2014, 15 in 2015) near Beaverlodge, Alberta and 31 fields (17 in 2014, 14 in 2015) near Lethbridge, Alberta.
Commodity canola fields were selected based on the proximity of honey bee apiaries and site access. 
28 of the 60 fields were stocked with honey bees at the corner or side of the field (mean: 0.6 hives/hectare, SD: 0.58) while 32 fields were unstocked. %range: 0.03 - 3.1 Apiaries were stationed at the edges of fields, often near to shrubs or tree-lines to act as a wind break.
14 of 31 of the fields near Lethbridge were watered using central-pivot irrigation systems.
Growers were also asked for canola variety information, but there was not enough replication to test for difference between varieties.
% Fields with central-pivot irrigation were mostly circular, but dryland (non-irrigated) fields were usually square or rectangular.

%Maps + climate graphs needed for publication
During 2015 and 2016, we also surveyed 35 hybrid seed canola fields (15 in 2015, 20 in 2016) near Lethbridge, Alberta, from June through August of each year, all of which had central-pivot irrigation
Seed fields were all stocked with honey bee hives at a rate of 3.6 hives/ha, with apiaries stationed in the corners of fields, and were also stocked with leafcutter bees in shelters throughout the field.
% Shelters used either ``standard" or ``double"  leafcutter bee stocking ($\approx$50,000 vs. 100,000 cocoons/ha), and shelters were placed at either ``standard" or ``double" densities (1.3 vs. 2.6 shelters/ha) in each field.
% Double stocking rates were only used in fields with double shelter density, creating three combinations of leafcutter bee stocking: ``standard", ``double shelter", and ``double shelter and double stocking".
All seed fields .
%Woudick 5,6 = 64 shelters (single), Woudick 2 = 113 shelters (double + bees), Woudick 3 = 128 shelters Graham 1 = 135 shelters
